\newpage
\section{Input Files}
\label{sec:input}
This section contains information on the format of \Langmuir input files.
Input files are just text files that you can edit with any text editor.
However, be warned that input files can be very long if they contain
    information on traps.
In this case, it is best to use a text editor capable of dealing with
    very large files.
Input files can also be manipulated using \LangmuirPython, as discussed
    in section ~\ref{sec:python}.
In \Langmuir, input files and checkpoint files are the same thing.
Periodically, a running simulation will save a checkpoint file.
You can use this checkpoint file to extend the simulation or change
    its parameters.
The \verb|#| symbol serves as a comment inside the input file.
Any text after the \verb|#| symbol is ignored.
The input file is divided into sections.
Sections always start with a header.
The valid section headers are shown below.

\begin{itemize}
    \item \verb|[Electrons]|
    \item \verb|[Holes]|
    \item \verb|[Defects]|
    \item \verb|[Traps]|
    \item \verb|[TrapPotentials]|
    \item \verb|[FluxState]|
    \item \verb|[RandomState]|
    \item \verb|[Parameters]|
\end{itemize}

The only required section is the \verb|[Parameters]| section,
    and it must be the last section in the input file.
Other sections do not have to be in any particular order.
Example input files are found in section~\ref{ssec:examples}.

\subsection{Site IDs}
    \label{ssec:sites}
    The position of an agent in the grid can be thought of as a 3-tuple
        of integers ($x_{i}$, $y_{i}$, $z_{i}$).
    This 3-tuple can be hashed into a single number called
        the site-id, $s_{i}$.
    The dimensions of the grid are $L_{x}$, $L_{y}$, and $L_{z}$.
    Note that $L_{x}$, $L_{y}$, and $L_{z}$ are the \verb|grid.x|,
        \verb|grid.y|, and \verb|grid.z| parameters discussed in
        section~\ref{ssec:parameters}.
    The following equations hold for site-ids, where all quantities
        are integers, and integer division applies.

    \begin{alignat}{3}
        \label{eqn:xrange}
        & 0 \leq & x_{i} < & L_{x} & x_{i} =& s_{i} \% L_{x} \\
        \label{eqn:yrange}
        & 0 \leq & y_{i} < & L_{y} & y_{i} =& s_{i} / L_{x} - (s_{i}/(L_{x}L_{y})) L_{y} \\
        \label{eqn:zrange}
        & 0 \leq & z_{i} < & L_{z} & z_{i} =& s_{i} / (L_{x}L_{y}) \\
        \label{eqn:srange}
        & 0 \leq & s_{i} < & L_{x} L_{y} L_{z} \quad & s_{i} =& L_{x} (y_{i} + z_{i} L_{y})+ x_{i}
    \end{alignat}

\newpage
\subsection{Agents}
    \label{ssec:agents}
    Electrons, holes, defects, and traps all follow the same format.
    Note that these sections are for providing information on
        electrons, etc.\ already present in the system before the
        simulation starts.
    This is typically the case when extending a run, or placing
        traps at well defined locations.
    You may leave these sections out.
    \Langmuir has the ability to place traps, defects, and carriers
        randomly if desired (see section~\ref{ssec:parameters}).

    It is very important that the parameters
        \verb|electron.percentage|, \verb|hole.percentage|,
        \verb|defect.percentage|, and \verb|trap.percentage|
        are consistent with these sections.
    For example, while the number of electrons in the \verb|Electrons|
        section can be less than the maximum number of electrons
        allowed by \verb|electron.percentage|, it can not exceed
        the max.
    If there is a problem, \langmuir will raise an error.

    The first line is the section header written in square brakets.
    The next line is always the number of elements to be read by
        \langmuir.
    For example, for the electrons, the second line is the number of
        electrons.
    The remaining lines are the site-ids for electrons, holes, defects,
        and traps.
    Site-id's are discussed in section~\ref{ssec:sites}.

    \begin{bashcode*}{gobble=8}
        [Electrons]    # section header
        2              # number of electrons
        100            # site-id of electron 1
        200            # site-id of electron 2
        [Holes]        # section header
        0              # number of holes
        [Defects]      # section header
        0              # number of defects
        [Traps]        # section header
        0              # number of traps
    \end{bashcode*}

\subsection{Trap Potentials}
    \label{ssec:trap}
    The \verb|[TrapPotentials]| section is very similar in structure to
        the \verb|[Trap]| section.
    The only difference is that instead of site-ids, one lists the
        trap potentials in units of \si{eV}.
    If present, the \verb|[TrapPotentials]| section must be the same
        size as the \verb|[Traps]| section.
    Note that if all traps have the same value, then this section
        can be omitted.
    In this case, the value used for trap potential is taken from the
        \verb|trap.potential| parameter (see section~\ref{ssec:parameters}).

    \begin{bashcode*}{gobble=8}
        [TrapPotentials]    # section header
        2                   # number of traps
        0.50                # trap potential of trap 1
        0.50                # trap potential of trap 2
    \end{bashcode*}

\newpage
\subsection{Flux State}
    \label{ssec:flux}
    The \verb|[FluxState]| is a list of 20 integers detailing the
        number of attempts and successes made by a flux agent.
    Examples of flux agents are the sources and drains.
    There are 10 different flux agents in \Langmuir.
    There are 2 source agents and 2 drain agents at $x_{i} = 0$ and
        $x_{i} = L_{x} - 1$, making a total of 8.
    The remaining 2 are an exciton source, and a recombination drain.
    You probably never have to edit this section.

    \begin{bashcode*}{gobble=8}
        # The codes should hopefully be easy to figure out...
        # ESLA = Electron Source Left Attempt
        # XDS  = Recombination Drain Success
        # etc...
        [FluxState]    # section header
        20             # number of flux agents
        0              # ESLA
        0              # ESLS
        0              # ESRA
        0              # ESRS
        0              # HSLA
        0              # HSLS
        0              # HSRA
        0              # HSRS
        0              # XSA
        0              # XSS
        0              # EDLA
        0              # EDLS
        0              # EDRA
        0              # EDRS
        0              # HDLA
        0              # HDLS
        0              # HDRA
        0              # HDRS
        0              # XDA
        0              # XDS
    \end{bashcode*}

\subsection{Random State}
    \label{ssec:random}
    The \verb|[RandomState]| is a very long list of integers that
        describe the exact state of the random number generator.
    Due to limitations of the combination of boost, stdlib, and qt,
        it must be on one line.
    You should never have to edit this section, other than deleting it.

    \begin{bashcode*}{gobble=8}
        [RandomState] # section header
        1371835351 1524755492 3319441753 617340572... # list of numbers
    \end{bashcode*}

\newpage
\subsection{Parameters}
    \label{ssec:parameters}
    The parameters section is a list of \verb|key=value| pairs that
        alter the behavior of the simulation.
    This section will often be the only section in an input file.
    It must be present, and it must be the last section in the text
        file.
    Below is a list of parameters and their descriptions.
    
    \input{sections/parameters}

\newpage
\subsection{Examples}
    \label{ssec:examples}
    This section contains sample input files.

    \subsubsection{Transistor}
    \begin{bashcode*}{gobble=8}
        [Parameters]
        simulation.type         = transistor

        grid.x                  = 1024
        grid.y                  = 256
        grid.z                  = 1

        iterations.real         = 500000
        iterations.print        = 1000

        electron.percentage     = 0.10
        seed.charges            = 1.00      # speed up equilibration

        voltage.right           = 5.00
        voltage.left            = 0.00

        coulomb.carriers        = true
        use.opencl              = true
    \end{bashcode*}

    \subsubsection{Solar Cell}
    \begin{bashcode*}{gobble=8}
        [Parameters]
        simulation.type         = solarcell

        grid.x                  = 256
        grid.y                  = 256
        grid.z                  = 1

        iterations.real         = 20000000  # much longer than transistor
        iterations.print        = 1000

        electron.percentage     = 0.10
        hole.percentage         = 0.10

        trap.percentage         = 0.50
        trap.potential          = 0.50
        seed.percentage         = 0.10

        voltage.right           = 9.00
        voltage.left            = 0.00

        source.rate             = 1e-3
        recombination.rate      = 1e-4

        coulomb.carriers        = true
        use.opencl              = true
    \end{bashcode*}

    \newpage
    \subsubsection{Scan}
    Set a variable equal to a list of values.  This works for any variable.
    See section~\ref{sec:python}.
    \begin{bashcode*}{gobble=8}
        [Parameters]
        ...
        voltage.right = [-2.0, -1.5, -1.0, -0.8, -0.6, -0.4, -0.2, 0.0]
        ...
    \end{bashcode*}   
    To generate input files.
    \begin{bashcode*}{gobble=8}
        adam@work: python scan.py --real 500000 --print 1000 --mode gen
    \end{bashcode*}
    To run \Langmuir in real time.
    \begin{bashcode*}{gobble=8}
        adam@work: python scan.py --real 500000 --print 1000 --mode scan
    \end{bashcode*}
    
    \subsubsection{Traps}
    \begin{bashcode*}{gobble=8}
        [Parameters]
        ...
        trap.percentage         = 0.50 # 50-percent traps
        seed.percentage         = 0.10 # 10-percent seeds
        trap.potential          = 0.05 #
        ...
    \end{bashcode*} 

    \subsubsection{Defects}
    \begin{bashcode*}{gobble=8}
        [Parameters]
        ...
        defect.percentage       = 0.50 # 50-percent defects
        defect.charge           = 0    # neutral defects
        ...
    \end{bashcode*}

    \subsubsection{Coulomb}
    \begin{bashcode*}{gobble=8}
        [Parameters]
        ...
        coulomb.carriers        = true # turn on coulomb interations
        use.opencl              = true # use GPU
        output.coulomb          = 10   # output energy every 10 iterations.print
        ...
    \end{bashcode*}
    To calculate coulomb energy of a checkpoint file you can use the
        python script coulomb.py.
    If the system is too big for the GPU you have to use coulomb.py.
    Or you can run \langmuir again.
    \begin{bashcode*}{gobble=8}
        [Parameters]
        ...
        iterations.real         =  0 # do not simulate anything
        output.coulomb          = -1 # output energy at the end
        ...
    \end{bashcode*}    
    